\begin{thebibliography}{9}

\bibitem{riyad16}
Al-Rousan, R., Sunar, M., Kolivand, H. (2016).  \emph{Interactive toon shading using mesh smoothing}. Int. J. Intelligent Systems Technologies and Applications. vol 15, 218-229.    

\bibitem{texbook}
Angel, E., Shreiner, D. (2012). \emph{Interactive Computer Graphics: A top-down approach using OpenGL}. Pearson.

\bibitem{Contours}
Baert, Jerone. Jeroen Baert's Blog, 3 Sept. 2010. \emph https://www.forceflow.be/thesis/thesis-code/. Suggestive Contours for Conveying Shape (princeton.edu)

\bibitem{decaudin96}
Decaudin, P. (1996). \emph{Cartoon-looking rendering of 3D scenes}

\bibitem{decarlo03}
DeCarlo, D., Finkelstein, A., Rusinkiewicz, S., \& Santella, A. (2003). \emph{Suggestive contours for conveying shape}. In ACM SIGGRAPH 2003 Papers (pp. 848–855).

\bibitem{gooch98}
Gooch, A., Gooch, B., Shirley, P., \& Cohen, E. (1998). \emph{A non-photorealistic lighting model for automatic technical illustration}. Proceedings of the 25th Annual Conference on Computer Graphics and Interactive Techniques, 447–452.

\bibitem{Stencil}
(2015) \emph {Stencil Testing}. https://learnopengl.com/Advanced-OpenGL/Stencil-testing

\bibitem{graf02}
Graf, C. (2002). \emph{NPR-Shading}.

\bibitem{lee06}
Lee, CH., Hao, X., Varshney, A. (2006). \emph{Geometry-dependent lighting.} IEEE Trans Vis Comput Graph. vol 12(2), 197-207. 

\bibitem{mitchell07}
Mitchell, J., Francke, M., \& Eng, D. (2007). \emph{Illustrative rendering in Team Fortress 2}. Proceedings of the 5th International Symposium on Non-Photorealistic Animation and Rendering, 71–76.

\bibitem{phong75}
Phong, B. T. (1975). \emph{Illumination for computer generated pictures}. Communications of the ACM, 18(6), 311–317.

\bibitem{saito90}
Saito, T., \& Takahashi, T. (1990). \emph{Comprehensible rendering of 3-D shapes}. Proceedings of the 17th Annual Conference on Computer Graphics and Interactive Techniques, 197–206. https://doi.org/10.1145/97879.97901
\end{thebibliography}
