\thechapter{Conclusions} 
Our implementation can produce a cartoon-style rendering from a variety of models and 
allows for customization, but when inspecting details of the model there are some obvious 
issues, especially with models that are not smooth.

The jagged lines produced by applying cel shading or applying rim lighting to models with 
lower vertex counts could potentially be fixed by increasing the vertex count to make the model 
smoother, but would make rendering the model much less efficient. Methods proposed By Riyad et 
al. to smooth the model vertices could also be used to improve rendering of models with rough 
edges \cite{riyad16}. 

Lighting, and rim lighting in particular, could be further improved by geometry dependent 
lighting methods introduced by Lee et al \cite{lee06}. This would enable automatic customization 
of the lighting to enhance particular aspects of the model and increase the overall quality of 
the image generated, and also give a more consistent appearance for rim lighting as the model 
would consist of smooth curves.

Cel shading textures could have been improved by defining a specific discrete range of colors 
to map the initial colours to, allowing for a larger variety of customization and more accurately 
coloured outputs. This is especially the case for models with textures that had colors that were 
not smoothly distributed.

The cartoon renderings produced from 3D models were not optimal in all cases, but models with 
smooth curves, colouring, and a large number of vertices produced more consistent and visually 
appealing results. Through further modification to the initial model the same simple techniques 
could be applied successfully to a larger variety of models.